MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-12 MAESTROeX_I/paper.tex
sign error
another sign error
add a TODO

@@

\subsection{Computing $w_0$ For Spherical Problems}
Recall that we want to solve
\begin{equation}
\frac{1}{r^2}\frac{\partial}{\partial r}(r^2 w_0) = \Sbar - \frac{1}{\gammaonebar p_0}\left(\frac{\partial p_0}{\partial t} + w_0\frac{\partial p_0}{\partial r}\right)
\end{equation}
First, note that $\partial p_0/\partial r = \rho_0 g$.
The key observation here is that we can compute $\partial p_0/\partial t$ directly instead of making complicated substitutions involving $\eta_\rho$ to eliminate it.
Let's discretize this as follows:
\begin{equation}
\frac{1}{r_j^2}\left[\left(r^2 w_0\right)_{j+\myhalf} - \left(r^2 w_0\right)_{j-\myhalf}\right] = 
\Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left[\left(\frac{\partial p_0}{\partial t}\right)_j + \left(\frac{w_{0,j-\myhalf}+w_{0,j+\myhalf}}{2}\right)(\rho_0 g)_j\right]
\end{equation}
Rearranging this to solve for $w_{0,j+\myhalf}$ gives us an explicit update:
\begin{equation}
\left[\frac{r_{j+\myhalf}^2}{r_j^2} - \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j+\myhalf} =
\left[\frac{r_{j-\myhalf}^2}{r_j^2} + \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j-\myhalf}
+ \Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left(\frac{\partial p_0}{\partial t}\right)_j
\end{equation}
As before, once $\rho_0$ falls below $\rho_{\rm cutoff}$, we hold $r^2 w_0$ constant.\\ \\
The interface to the routine in the algorithm description is
{\bf Make $\mathbf{w_0}$}$[\rho_0,p_0,\partial p_0/\partial t,\gammaonebar,\Sbar] \rightarrow [w_0]$

>>>>

TODO list:
\begin{itemize}
\item Weak scaling tests of original algorithm, comparing MAESTRO to MAESTROeX.  Use cori knl, 4 MPI per node, 16 threads per MPI
\item Run at effective $512^3$ resolution (maybe to ignition?... need to see how max T trends go) (1) classic MAESTRO, (2) MAESTROeX with original algorithm, (3) MAESTROeX with new temporal integrator, (4) MAESTROeX with new temporal integrator and irregular dr, (5) MAESTROeX with original algorithm and 3-levels of AMR, (6) MAESTROeX with new temporal integrator and 3 levels of AMR.
\item (perhaps) a demonstration of what goes wrong when you don't split the velocity dynamics in the projection
\end{itemize}

@@

\subsection{Computing $w_0$ For Spherical Problems}
Recall that we want to solve
\begin{equation}
\frac{1}{r^2}\frac{\partial}{\partial r}(r^2 w_0) = \Sbar - \frac{1}{\gammaonebar p_0}\left(\frac{\partial p_0}{\partial t} + w_0\frac{\partial p_0}{\partial r}\right)
\end{equation}
First, note that $\partial p_0/\partial r = -\rho_0 g$.
The key observation here is that we can compute $\partial p_0/\partial t$ directly instead of making complicated substitutions involving $\eta_\rho$ to eliminate it.
Let's discretize this as follows:
\begin{equation}
\frac{1}{r_j^2}\left[\left(r^2 w_0\right)_{j+\myhalf} - \left(r^2 w_0\right)_{j-\myhalf}\right] = 
\Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left[\left(\frac{\partial p_0}{\partial t}\right)_j - \left(\frac{w_{0,j-\myhalf}+w_{0,j+\myhalf}}{2}\right)(\rho_0 g)_j\right]
\end{equation}
Rearranging this to solve for $w_{0,j+\myhalf}$ gives us an explicit update:
\begin{equation}
\left[\frac{r_{j+\myhalf}^2}{r_j^2} - \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j+\myhalf} =
\left[\frac{r_{j-\myhalf}^2}{r_j^2} + \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j-\myhalf}
+ \Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left(\frac{\partial p_0}{\partial t}\right)_j
\end{equation}
As before, once $\rho_0$ falls below $\rho_{\rm cutoff}$, we hold $r^2 w_0$ constant.\\ \\
The interface to the routine in the algorithm description is
{\bf Make $\mathbf{w_0}$}$[\rho_0,p_0,\partial p_0/\partial t,\gammaonebar,\Sbar] \rightarrow [w_0]$
